Fermi and eROSITA bubbles

### 2021-12-16 paper.tex
update

  \textsc{gamer-sr} adopts a new algorithm \citep{tseng2021} to convert between\
  primitive ($p$, $\rho$, $U^{j}$) and conserved variables, ($D$, $M^{j}$, $\tilde{E}$)\
  significantly reducing numerical error caused by catastrophic cancellations\
  that commonly occur within the regions with high Mach number. e.g., jet-ISM interaction zones.

  \textsc{gamer-sr} also adaptively and locally reduce the min-mod coefficient\
  \citep{tseng2021} within the failed patch group.\
  Doing so provides an elegant way to avoid the use of pressure/density floor,\
  being unnatural but widely used in almost publicly available codes.

\subsection{Initial conditions for the Fermi and eROSITA bubbles}
  The simulation box is $14\times14\times28$ kpc, slightly larger than the size of eROISTA bubbles,\
  with a root grid $N=16\times16\times32$. We resolve the jet source located at the center of the simulation domain,\
  cells are refined to level 11, leading to a finest spatial resolution of 0.4 pc.\

  To save computational costs, we restrict the refinement level is 7 within the cold disk so that\
  a molecular cloud can be adequately resolved by approximately 30 cells along their diameter, 100 pc.

\begin{enumerate}
  \item Assumptions on hydrodynamics:

  \item Assumptions on gravity:
    \begin{enumerate}
      \item We use the potential of isothermal slab, symmetric about $z=0$ and\
            supported by gas pressure and by under its own self-gravity,\
            to mimic the realistic potential of Galactic bulge.
%      \item We still use Newtonian gravity, as the relativistic fluid ejected by the jet source\
%            is quickly slowed down by heavy disk in a short time, and the relativistic fluid\
%            accounts for a little minority of total mass inside the simulation box.
      \item The ISM disk and atmosphere are subjected to the fixed external potential\
            due to a disk bulge and dark matter halo.
      \item In addition to the gravitational interaction, we ignore other interactions between stars and gases.
      \item We also ignore the self-gravity of the ISM disk and of the atmosphere.
      \item We ignore the centrifugal force of Milky Way rotation acting on the bubbles.
      \item We use the potential of isothermal slab to mimic the gravitational potential due to the stellar bulge.
      \item The interface between cold ISM disk and atmosphere is parallel to the Galactic plane and is pressure balanced.
    \end{enumerate}
\end{enumerate}
We simulate 3D special relativistic hydrodynamics with passive CR injections from the GC using\
the special hydrodynamics GPU code \textsc{gamer-sr} \citep{tseng2021}.

\textsc{gamer-sr} solves mass and energy-momentum conservation laws of a special relativistic ideal fluid\
with CR.

@@

@@

\end{enumerate}
\subsection{Jet injection}
 \begin{enumerate}
    \item Why the overall structure is insensitive to jet direction?
      \begin{enumerate}
        \item Jet source size.
        \item Cold disk.
        \item Large pressure gradient along z-dircetion.
      \end{enumerate}
 \end{enumerate}

>>>>

  \textsc{gamer-sr} adopts a new algorithm \citep{tseng2021} to convert between\
  primitive ($\rho$, $U^{j}$, $p$) and conserved variables ($D$, $M^{j}$, $\tilde{E}$),\
  significantly reducing numerical error caused by catastrophic cancellations\
  that commonly occur within the regions with high Mach number. e.g., jet-ISM interaction zones.

  \textsc{gamer-sr} also adaptively and locally reduce the min-mod coefficient\
  \citep{tseng2021} within the failed patch group.\
  Doing so provides an elegant way to avoid the use of pressure/density floor,\
  being unnatural but widely used in almost publicly available codes.\

@@

  We model the external and fixed gravity of the Milky Way by prescribing a\
  plane parallel self-gravitating isothermal slab, symmetry about the mid-plane $z=0$,\
  in a simulation box size of\
  $14\times14\times28$ kpc, slightly larger than the size of eROISTA bubbles.

  In our 3D simulation, the Galactic potential can be written as

  \begin{equation}
    \Phi_{\text{total}} = \Phi_{\text{disk}} + \Phi_{\text{halo}},
  \end{equation}

  where $\Phi_{\text{halo}}=v^2_{\text{halo}}\ln\left(z^2+d^2_{\text{h}}\right)$\

  is dark logarithmic halo potential,

  \begin{equation}
    \Phi_{\text{disk}}=\
    2\sigma^2_{\text{disk}}\
    \ln\cosh\left(z\sqrt{\frac{2\pi G\rho_{\text{disk}}^{\text{peak}}}{\sigma^2_{\text{disk}}}}\right),
  \end{equation}

  is the potential of a plane-parallel isothermal slab.

  The slab is used to mimic the gravity contributed by the stars within the Galactic plane,\
  the  thus

  We mimic the galactic potential by using

  The potential of slab is mainly contributed by the stars within the Galactic center.

  The AMR base level is covered by $16\times16\times32$ root grids, refined progressively on the plane $z=0$\
  , with the outflow boundary condition.

  confined by an external dark halo potential.

  We use three components (1) cold ISM disk (2) hot gas ambient (3) stellar disk\
  to locally mimic the environment near the GC (i.e. no galactic rotation).\

  The density distributions of ISM disk and hot gas ambient are derived from\
  hydrostatic equilibrium within the fixed external potential.

  We use the potential of isothermal slab, symmetric about $z=0$, and\
  supported by gas pressure and by its own self-gravity,\
  to mimic the realistic potential of Galactic bulge.

\begin{enumerate}
  \item Assumptions on gravity:
    \begin{enumerate}
      \item We use the potential of isothermal slab, symmetric about $z=0$ and\
            supported by gas pressure and by under its own self-gravity,\
            to mimic the realistic potential of Galactic bulge.
      \item The ISM disk and atmosphere are subjected to the fixed external potential\
            due to a disk bulge and dark matter halo.
      \item In addition to the gravitational interaction, we ignore other interactions between stars and gases.
      \item We also ignore the self-gravity of the ISM disk and of the atmosphere.
      \item We ignore the centrifugal force of Milky Way rotation acting on the bubbles.
      \item We use the potential of isothermal slab to mimic the gravitational potential due to the stellar bulge.
      \item The interface between cold ISM disk and atmosphere is parallel to the Galactic plane and is pressure balanced.
    \end{enumerate}
\end{enumerate}

@@

\end{enumerate}

\subsection{Cold disk}
  We restrict the refinement level is 7 within the cold disk so that\
  a molecular cloud can be adequately resolved by approximately 30 cells along their diameter, 100 pc.\

\subsection{Jet injection}
  We resolve the jet source located at the center of the simulation domain,\
  cells are refined to level 11, leading to a finest spatial resolution of 0.4 pc.\

 \begin{enumerate}
    \item Why the overall structure is insensitive to jet direction?
      \begin{enumerate}
        \item Jet source size.
        \item Cold disk.
        \item Large pressure gradient along z-dircetion.
      \end{enumerate}
 \end{enumerate}
